---
title: "TidyTemplate"
date: 2024-02-12
output: html_document
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)

```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2024-02-13")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}
# gender data

valentine_gender <- tt$gifts_gender %>%
  pivot_longer(-Gender, 
               names_to = "Gift", 
               values_to = "Percent") %>%
  mutate(Gift = factor(Gift)) %>%
  mutate(Gender = factor(Gender)) %>%
  group_by(Gift) %>%
  mutate(Difference = Percent - lag(Percent)) %>%
  ungroup()

# age data  
valentine_age <- tt$gifts_age %>%
  pivot_longer(-Age, 
               names_to = "Gift", 
               values_to = "Percent") %>%
  mutate(across(where(is.character), as.factor)) %>%
  group_by(Gift) %>%
  mutate(Difference = Percent - lag(Percent, n = 5)) %>%
  fill(Difference, .direction = "up") %>%
  mutate(IncreaseWithAge = case_when(Difference > 0 ~ TRUE,
                                    is.na(Difference) ~ NA,
                                    .default = FALSE))
  

valentine_age

```


# Visualize Gender

Using your processed dataset, create your unique visualization.

```{r Visualize}
valentine_gender %>%
  ggplot(aes(x = fct_reorder(Gift, Difference, .na_rm = TRUE), y = Percent, fill = Gender)) +
  geom_col(position = "dodge") +
  coord_flip() +
  labs(title = "Valentine's Day Gift",
       subtitle = "ordered by difference between genders, women buy more often to men buy more often",
       x = "Gift Type",
       y = "Percent",
       caption = "Data Source: Tidy Tuesday") +
  scale_fill_brewer(palette = "Accent") +
  theme_minimal()


valentine_gender %>%
  ggplot(aes(x = Gift, y = Percent, fill = Gender)) +
  geom_col() +
  facet_grid(rows = vars(Gender)) +
  labs(title = "Valentine's Day Gift",
       x = "Gift Type",
       y = "Percent",
       caption = "Data Source: Tidy Tuesday") +
  scale_fill_brewer(palette = "Accent") +
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))
```
# Visualize Ages

Using your processed dataset, create your unique visualization.
```{r}
valentine_age %>%
  ggplot(aes(x = Age, y = Percent, group = Gift, color = Gift, linewidth = IncreaseWithAge)) +
  geom_line() +
  scale_linewidth_manual(values = c(0.5, 1.5)) +
  guides(linewidth = "none") +
  scale_color_brewer(palette = "Accent") +
    labs(title = "Valentine's Day Gifts by Age",
       subtitle = "bold line indicates an increase between starting and ending age groups",   
       x = "Age Bracket",
       y = "Percent",
       caption = "Data Source: Tidy Tuesday") +
  theme_bw()

```



# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png")

```
